### 2019-08-10 paper/paper.tex
fixing spelling mistakes, final examination of the paper, added one article to the .bib

\section{Introduction}
When we face a multi-choice question answering (QA) problem where we have to choose the most probable answer, we arrive at it with prior information and knowledge. for instance, we have some kind of a

@@

While in some cases the state of the art machine-learning methods which were trained on massive amount of data to infer prediction roles
outperforms human-level by a large margin (e.g. SQUAD 2.0 \cite{rajpurkar2018know}),
In the field of common sense reasoning  \cite{talmor2018commonsenseqa} state of the art algorithms fail to generalize and are yet inferior to human level performance.
This is due to two main reasons: first, is that when using algorithms such as fine-tuning a pre-trained language model, it is likely that this knowledge (common sense) does not exist explicitly in the pre training corpus, and second, is due to the fact that creating massive datasets for this purpose solely is hard, and developed only in the last years mostly by crowdsourcing.

@@

BERT's input representation (figure \ref{bert_input_repr}) uses WordPeace \cite{wu2016google} tokenization which is a data driven method that aims to achieve a balance between vocabulary size and out-of-vocab words. This way BERT stores only 30K vocabulary words, yet very rarely encounters out-of-vocab words when tokenizing English texts. Two special token are added for each sentence, a start token [CLS] and an end token [SEP]. If the input contains two sentences another [SEP] token is added in between the sentences. Due to the fact that Transformers do not encode the sequential nature of their inputs a segment ids and position embeddings are added as well to the input.

@@

% $$
% P := \text{\textit{Learned parameter}}
% $$
% $$
% CT_{i,j} := \text{\textit{Classifier Tokens Concatened}}
% $$
% $$
% S'_{i,j} := P \cdot CT_{i,j}
% $$
% $$
% \text{\textit{Score}}_{i,j} := \frac{S'_{i,j} + (1 - S'_{j,i})}{2}
% $$

>>>>

\section{Introduction}
When we face a multi-choice problem where we have to choose the most 
probable answer we arrive to it with prior information and knowledge. e.g,  example, we have some kind of a language model that tells us if sentence A is more probable then sentence B, and we have knowledge about the physical world which tells us what is more possible or probable.

@@

While in some cases the state of the art machine-learning methods which were trained on massive amount of data to infer prediction roles
outperforms human-level by a large margin (e.g. SQUAD 2.0 \cite{rajpurkar2018know}),
In the field of common sense reasoning  \cite{talmor2018commonsenseqa} state of the art algorithms fail to generalize and are yet inferior to human level performance.
This is due to two main reasons: first, is that when using algorithms such as fine-tuning a pre-trained language model, it is likely that this knowledge (common sense) does not exist explicitly in the pre-training corpus. And second, is due to the fact that creating massive datasets for this purpose solely is hard, and developed only in the last years mostly by crowdsourcing.

@@

BERT's input representation (figure \ref{bert_input_repr}) uses WordPeace \cite{wu2016google} tokenization which is a data driven method that aims to achieve a balance between vocabulary size and out-of-vocabulary words. This way BERT stores only 30K vocabulary words, yet very rarely encounters out-of-vocabulary words when tokenizing English texts. Two special token are added for each sentence, a start token [CLS] and an end token [SEP]. If the input contains two sentences another [SEP] token is added in between the sentences. Due to the fact that Transformers do not encode the sequential nature of their inputs a segment ids and position embeddings are added as well to the input.

@@
